---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wtfdbg

<!-- badges: start -->
<!-- badges: end -->

This is an intentionally buggy package to facilitate practice of debugging
other's code for the RStudio Conference Workshop _What They Forgot To Teach You About R_.


The `fruit_avg()` function is from Jenny Bryan's rstudio::conf(2020) keynote
_Object of type 'closure' is not subsettable_ <https://github.com/jennybc/debugging>.

Associated exercises are at <https://github.com/rstats-wtf/wtf-debugging>.

## Installation

You can install the development version of `wtfdbg` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rstats-wtf/wtfdbg")
```

## This works


```{r example-works}
library(wtfdbg)
fruit_avg(fruit, "berry")
```

## This does not

```{r example-fail, error = TRUE}
fruit_avg(fruit, "peach")
```


Can you use debugging tools to figure out why?
